StanResultsSummary

### 2020-09-25 Results Archive/StanResultsSummary_relaxedgamma5.Rmd
updated code

---
title: "StanResultsSummary"
author: "Kevin Murgas"
date: "4/24/2020"
output: pdf_document
---
Summary of Stan Model Fit Results: Full-Scale (850K sites)
\newline Relaxed Gamma priors (using relaxed gamma fits with x2 variance)
```{r Setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
library(knitr)
```

```{r Load, echo=FALSE, include=FALSE}
setwd("/Users/kevinmurgas/Documents/Data+ project/EPIC data")
load("myFA_bulkonly.Rdata")
load("FullResultsTCGA_relaxedgamma.Rdata")

@@

# plot mu,betaT,sigmaE,sigmaP,sigmaPT,sigmaT
fBG <- function(x, a, m1, s1, m2, s2) a*dnorm(x,m1,s1) + (1-a)*dnorm(x,m2,s2)
pM <- ggplot(data.frame(mu=mu_full$p50), aes(x=mu)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("Mu") + xlim(c(-5,5)) + geom_vline(xintercept=mean(mu_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) fBG(x,0.3557,-3.0675, 0.75214,1.1290, 1.39197)/0.1906566,geom="line",color="red")
pB <- ggplot(data.frame(betaT=betaT_full$p50), aes(x=betaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("BetaT") + xlim(c(-5,5)) + geom_vline(xintercept=mean(betaT_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dcauchy(x,-0.04051, 0.38660)/0.82336,geom="line",color="red")
pE <- ggplot(data.frame(sigmaE=sigmaE_full$p50), aes(x=sigmaE)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaE") + xlim(c(0,2)) + geom_vline(xintercept=mean(sigmaE_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x,2,2)/0.7357589, geom="line",color="red")
pP <- ggplot(sigma_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaP") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[1], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 3.4016, 9.5057)/2.3641, geom="line",color="red")
pPT <- ggplot(sigma_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaPT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 2.5210, 3.2948)/1.0097, geom="line",color="red")
pT <- ggplot(sigma_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 4.2574, 14.370)/3.0964, geom="line",color="red")

@@

# plot the log sigmas
pP <- ggplot(logsig_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaP)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[1], linetype="dotted") + theme_bw()  + stat_function(fun=function(x) dgamma(exp(x), 3.4016, 9.5057)/2.3641, geom="line",color="red")
pPT <- ggplot(logsig_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaPT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 2.5210, 3.2948)/1.0097, geom="line",color="red")
pT <- ggplot(logsig_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 4.2574, 14.370)/3.0964, geom="line",color="red")
# and log ratios
pPPTr <- ggplot(logRatio_df, aes(x=PPTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"PT)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[1], linetype="dotted") + theme_bw()
pPTr <- ggplot(logRatio_df, aes(x=PTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[2], linetype="dotted") + theme_bw()
pPTTr <- ggplot(logRatio_df, aes(x=PTTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"PT/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[3], linetype="dotted") + theme_bw()

>>>>

---
title: "StanResultsSummary"
author: "Kevin Murgas"
date: "4/25/2020"
output: pdf_document
---
Summary of Stan Model Fit Results: Full-Scale (850K sites)
\newline Relaxed Gamma priors (using relaxed gamma fits with x5 variance)
```{r Setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
library(knitr)
```

```{r Load, echo=FALSE, include=FALSE}
setwd("/Users/kevinmurgas/Documents/Data+ project/EPIC data")
load("myFA_bulkonly.Rdata")
load("FullResultsTCGA_relaxedgamma5.Rdata")

@@

# plot mu,betaT,sigmaE,sigmaP,sigmaPT,sigmaT
fBG <- function(x, a, m1, s1, m2, s2) a*dnorm(x,m1,s1) + (1-a)*dnorm(x,m2,s2)
pM <- ggplot(data.frame(mu=mu_full$p50), aes(x=mu)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("Mu") + xlim(c(-5,5)) + geom_vline(xintercept=mean(mu_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) fBG(x,0.3557,-3.0675, 0.75214,1.1290, 1.39197)/0.1906566,geom="line",color="red")
pB <- ggplot(data.frame(betaT=betaT_full$p50), aes(x=betaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("BetaT") + xlim(c(-5,5)) + geom_vline(xintercept=mean(betaT_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dcauchy(x,-0.04051, 0.96650)/0.32934,geom="line",color="red")
pE <- ggplot(data.frame(sigmaE=sigmaE_full$p50), aes(x=sigmaE)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaE") + xlim(c(0,2)) + geom_vline(xintercept=mean(sigmaE_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x,2,2)/0.7357589, geom="line",color="red")
pP <- ggplot(sigma_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaP") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[1], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 2.2298, 4.8674)/1.6384, geom="line",color="red")
pPT <- ggplot(sigma_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaPT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 1.8166, 1.7689)/0.70791, geom="line",color="red")
pT <- ggplot(sigma_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 2.6144, 7.1221)/2.1250, geom="line",color="red")

@@

# plot the log sigmas
pP <- ggplot(logsig_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaP)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[1], linetype="dotted") + theme_bw()  + stat_function(fun=function(x) dgamma(exp(x), 2.2298, 4.8674)/1.6384, geom="line",color="red")
pPT <- ggplot(logsig_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaPT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 1.8166, 1.7689)/0.70791, geom="line",color="red")
pT <- ggplot(logsig_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 2.6144, 7.1221)/2.1250, geom="line",color="red")
# and log ratios
pPPTr <- ggplot(logRatio_df, aes(x=PPTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"PT)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[1], linetype="dotted") + theme_bw()
pPTr <- ggplot(logRatio_df, aes(x=PTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[2], linetype="dotted") + theme_bw()
pPTTr <- ggplot(logRatio_df, aes(x=PTTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"PT/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[3], linetype="dotted") + theme_bw()

### 2020-09-25 Results Archive/StanResultsSummary_relaxedinvgamma.Rmd
updated code

---
title: "StanResultsSummary"
author: "Kevin Murgas"
date: "4/25/2020"
output: pdf_document
---
Summary of Stan Model Fit Results: Full-Scale (850K sites)
\newline Relaxed Gamma priors (using relaxed gamma fits with x5 variance)
```{r Setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
library(knitr)
```

```{r Load, echo=FALSE, include=FALSE}
setwd("/Users/kevinmurgas/Documents/Data+ project/EPIC data")
load("myFA_bulkonly.Rdata")
load("FullResultsTCGA_relaxedgamma5.Rdata")

@@

# plot mu,betaT,sigmaE,sigmaP,sigmaPT,sigmaT
fBG <- function(x, a, m1, s1, m2, s2) a*dnorm(x,m1,s1) + (1-a)*dnorm(x,m2,s2)
pM <- ggplot(data.frame(mu=mu_full$p50), aes(x=mu)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("Mu") + xlim(c(-5,5)) + geom_vline(xintercept=mean(mu_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) fBG(x,0.3557,-3.0675, 0.75214,1.1290, 1.39197)/0.1906566,geom="line",color="red")
pB <- ggplot(data.frame(betaT=betaT_full$p50), aes(x=betaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("BetaT") + xlim(c(-5,5)) + geom_vline(xintercept=mean(betaT_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dcauchy(x,-0.04051, 0.96650)/0.32934,geom="line",color="red")
pE <- ggplot(data.frame(sigmaE=sigmaE_full$p50), aes(x=sigmaE)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaE") + xlim(c(0,2)) + geom_vline(xintercept=mean(sigmaE_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x,2,2)/0.7357589, geom="line",color="red")
pP <- ggplot(sigma_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaP") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[1], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 2.2298, 4.8674)/1.6384, geom="line",color="red")
pPT <- ggplot(sigma_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaPT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 1.8166, 1.7689)/0.70791, geom="line",color="red")
pT <- ggplot(sigma_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 2.6144, 7.1221)/2.1250, geom="line",color="red")

@@

# plot the log sigmas
pP <- ggplot(logsig_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaP)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[1], linetype="dotted") + theme_bw()  + stat_function(fun=function(x) dgamma(exp(x), 2.2298, 4.8674)/1.6384, geom="line",color="red")
pPT <- ggplot(logsig_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaPT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 1.8166, 1.7689)/0.70791, geom="line",color="red")
pT <- ggplot(logsig_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 2.6144, 7.1221)/2.1250, geom="line",color="red")
# and log ratios
pPPTr <- ggplot(logRatio_df, aes(x=PPTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"PT)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[1], linetype="dotted") + theme_bw()
pPTr <- ggplot(logRatio_df, aes(x=PTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[2], linetype="dotted") + theme_bw()
pPTTr <- ggplot(logRatio_df, aes(x=PTTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"PT/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[3], linetype="dotted") + theme_bw()

>>>>

---
title: "StanResultsSummary"
author: "Kevin Murgas"
date: "4/25/2020"
output: pdf_document
---
Summary of Stan Model Fit Results: Full-Scale (850K sites)
\newline Inverse-Gamma priors (using relaxed inv-gamma fits with x2 variance)
```{r Setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
library(knitr)
```

```{r Load, echo=FALSE, include=FALSE}
setwd("/Users/kevinmurgas/Documents/Data+ project/EPIC data")
load("myFA_bulkonly.Rdata")
load("FullResultsTCGA_relaxedinvgamma.Rdata")

@@

# plot mu,betaT,sigmaE,sigmaP,sigmaPT,sigmaT
fBG <- function(x, a, m1, s1, m2, s2) a*dnorm(x,m1,s1) + (1-a)*dnorm(x,m2,s2)
dIG <- function(x, a, b) 1/(b*gamma(a))*(b/x)^(a+1)*exp(-b/x)
pM <- ggplot(data.frame(mu=mu_full$p50), aes(x=mu)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("Mu") + xlim(c(-5,5)) + geom_vline(xintercept=mean(mu_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) fBG(x,0.3557,-3.0675, 0.75214,1.1290, 1.39197)/0.1906566,geom="line",color="red")
pB <- ggplot(data.frame(betaT=betaT_full$p50), aes(x=betaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("BetaT") + xlim(c(-5,5)) + geom_vline(xintercept=mean(betaT_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dcauchy(x,-0.04051, 0.38660)/0.823357,geom="line",color="red")
pE <- ggplot(data.frame(sigmaE=sigmaE_full$p50), aes(x=sigmaE)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaE") + xlim(c(0,2)) + geom_vline(xintercept=mean(sigmaE_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dIG(x,1,1)/0.54134, geom="line",color="red")
pP <- ggplot(sigma_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaP") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[1], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dIG(x, 3.7350, 1.0694)/2.9791,geom="line",color="red")
pPT <- ggplot(sigma_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaPT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dIG(x, 2.4884, 1.2601)/1.4368,geom="line",color="red")
pT <- ggplot(sigma_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dIG(x, 4.8358, 1.1529)/3.9851,geom="line",color="red")

@@

# plot the log sigmas
pP <- ggplot(logsig_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaP)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[1], linetype="dotted") + theme_bw()  + stat_function(fun=function(x) dIG(exp(x), 3.7350, 1.0694)/2.9791, geom="line",color="red")
pPT <- ggplot(logsig_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaPT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dIG(exp(x), 2.4884, 1.2601)/1.4368, geom="line",color="red")
pT <- ggplot(logsig_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dIG(exp(x), 4.8358, 1.1529)/3.9851, geom="line",color="red")
# and log ratios
pPPTr <- ggplot(logRatio_df, aes(x=PPTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"PT)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[1], linetype="dotted") + theme_bw()
pPTr <- ggplot(logRatio_df, aes(x=PTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[2], linetype="dotted") + theme_bw()
pPTTr <- ggplot(logRatio_df, aes(x=PTTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"PT/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[3], linetype="dotted") + theme_bw()
